Video Doesn't Lie

### 2016-05-02 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
add figure builds

## Acknowledgments
- [NSF BCS-1238599](http://www.nsf.gov/awardsearch/showAward?AWD_ID=1238599&HistoricalAwards=false)
- [NICHD U01-HD-076595](https://projectreporter.nih.gov/project_info_description.cfm?aid=8531595&icde=15908155&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC)
- [Society for Research in Child Development (SRCD)](http://srcd.org)
- NYU Libraries, ITS, IRB, and OSP

@@

## [Datavyu](http://datavyu.org) makes video coding reproducible
- Raw research video must be coded
- [Datavyu.org](http://datavyu.org) = free, [open source](https://github.com/databrary/datavyu) coding tool
- Add codes, annotations time-locked to video segments
- Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts) reproducible workflows

----
<div class="centered">
<a href="http://datavyu.org/user-guide/index.html">
<img src="http://datavyu.org/user-guide/_images/annotated-datavyu-desktop.png" width=800px>
</a>
</div>

## Reproducible video coding
<div class="centered">
<img src="img/crawl-1-hand-fall.jpg">

@@

----
<div class="centered">
<img src="img/timeline-crawl-1.jpg">

[[@ddff6ac6-cd1b-4365-89aa-70ea654b4ed9]](http://dx.doi.org/10.17910/B7MW2K)
</div>
----
<div class="centered">
<img src="img/datavyu-ss-bridge-crawl-1-trial10.jpg" width=1000px>

[[@ddff6ac6-cd1b-4365-89aa-70ea654b4ed9]](http://dx.doi.org/10.17910/B7MW2K)
</div>
----
<div class="centered">
<img src="img/databrary-vol-5-materials.jpg" width=1000px>

@@

## Securing permission to share while limiting access {.flexbox .vcenter}
<div class="centered">
<video width="640" height="480" controls>
  <source src="https://databrary.org/video/example-video-1.mp4" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>

## Databrary enhances reproducibility
- "Active" curation of data **as it is collected**
- Organize, share, standardized participant metadata
- Sharing based on 
    + user access level
    + participant permission

@@

@@

- Video uniquely captures complexity & richness of behavior
- Databrary securely stores, shares video + metadata
- Databrary and Datavyu enhance reproducibility of video-based research
- Databrary makes psychological science more transparent & reproducible

>>>>

## Acknowledgments
- [NSF BCS-1238599](http://www.nsf.gov/awardsearch/showAward?AWD_ID=1238599&HistoricalAwards=false)
- [NICHD U01-HD-076595](https://projectreporter.nih.gov/project_info_description.cfm?aid=8531595&icde=15908155&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC)
- [Society for Research in Child Development (SRCD)](http://srcd.org)
- NYU Libraries, NYU IT, IRB, and OSP

@@

## [Datavyu](http://datavyu.org) makes video coding reproducible

- Raw research video must be coded
- [Datavyu.org](http://datavyu.org) = free, [open source](https://github.com/databrary/datavyu) coding tool
- Add codes, annotations time-locked to video segments
- Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts) reproducible workflows

----

<div class="centered">
<a href="http://datavyu.org/user-guide/index.html">
<img src="http://datavyu.org/user-guide/_images/annotated-datavyu-desktop.png" width=1000px>
</a>
</div>

## Datavyu facilitates reproducible video coding

<div class="centered">
<img src="img/crawl-1-hand-fall.jpg" height=550px>

@@

----

<div class="centered">
<img src="img/timeline-crawl-0.jpg" height=550px>
</div>

----

<div class="centered">
<img src="img/timeline-crawl-1.jpg" height=550px>
</div>

----

<div class="centered">
<img src="img/datavyu-ss-bridge-crawl-1-trial10.jpg" height=550px>
</div>

----

<div class="centered">
<img src="img/databrary-vol-5-materials.jpg" width=1000px>

@@

- "Active" curation of data **as it is collected**
- Organize, share, standardized participant metadata
- Sharing based on 
    + user access level
    + participant permission

@@

----

<div class="centered">
<img src="img/vol-5-spreadsheet-0.jpg">
</div>

----

<div class="centered">
<img src="img/vol-5-spreadsheet-1.jpg">
</div>

----

<div class="centered">
<img src="img/vol-5-spreadsheet-2.jpg">
</div>

----

<div class="centered">
<img src="img/vol-5-spreadsheet-3.jpg">
</div>

----

<div class="centered">
<img src="img/vol-5-spreadsheet-4.jpg">
</div>

## Standardized -- reproducible -- release levels

<a href="https://databrary.org/access/guide/investigators/release/release-levels.html">
<div class="centered">
<img src="img/release-levels.jpg">
</a>
</div>

@@

- Video uniquely captures complexity & richness of behavior
- Databrary securely stores, shares video + metadata
- Databrary and Datavyu enhance reproducibility of video-based research
- Databrary makes psychological science more transparent & reproducible
- <http://github.com/databrary/presentations/nyu-data-science-reproducibility-16>

## To boldly go where no science has gone before...

- Reproducibility of numerical computation ≠ 
- Reproducibility of behavioral measures, manipulations
- **All** behavioral researchers should 
    + share reproducible workflows of data, analyses *AND*
    + videos of behavioral measures, displays
